gss marriage politics analysis

### 2023-04-20 outputs/paper/paper.qmd
updated attempted model and titles for graphs and tables

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

>>>>

## Marital Status and Cohort

```{r}
#| include: false
#| message: false
#### Creating Graph for comparison 2021 respondent's birth cohort against marital status ####
cohort_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "# of Respondents ",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") + 
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false
#### Creating Graph for comparison 2018 respondent's birth cohort against marital status ####
cohort_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "# of Respondents ",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") + 
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2016 respondent's birth cohort against marital status ####
cohort_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(legend.position = "none")+
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2014 respondent's birth cohort against marital status ####
cohort_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "2014-2021 Comparisons of Birth Cohort Against Respondent Marital Status"
#### Using Patchwork Package to Combine Two Graphs ####
(cohort_marital_2021) + (cohort_marital_2018) + (cohort_marital_2016) + (cohort_marital_2014) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

## Marital Status and Self-Ascribed Belonging to Political Parties

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2021 respondent's political party identity against marital status ####
partyid_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identity",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false
#### Creating Graph for comparison 2018 respondent's political party identity against marital status ####
partyid_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identity",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2016 respondent's political party identity against marital status ####
partyid_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identity",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2014 respondent's political party identity against marital status ####
partyid_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identity",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size=6)) 
```

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "2014-2021 Comparisons of Political Party Identity Against Respondent's Marital Status"
#### Using Patchwork Package to Combine Two Graphs ####
(partyid_marital_2021) + (partyid_marital_2018) + (partyid_marital_2016) + (partyid_marital_2014)+ 
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-4
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2021 Respondents"

cleaned_gss_2021|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")

```{r}
#| echo: false
#| warning: false
#| label: tbl-5
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2018 Respondents"

cleaned_gss_2018|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-6
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2016 Respondents"

cleaned_gss_2016|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-7
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2014|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

## Marital Status and Self-Ascribed Placement on Political Spectrum

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2021 respondent's political spectrum identity against marital status ####
polviews_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2018 respondent's political spectrum identity against marital status ####
polviews_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2016 respondent's political spectrum identity against marital status ####
polviews_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph for comparison 2024 respondent's political spectrum identity against marital status ####
polviews_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "2014-2021 Comparisons of Birth Cohort Against Respondent Marital Status"
#### Using Patchwork Package to Combine four Graphs ####
(polviews_marital_2021) + (polviews_marital_2018) + (polviews_marital_2016) + (polviews_marital_2014)+ 
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-8
#| tbl-cap: "Marital Status vs. Self-Ascribed Placement on Political of 2014 Respondents"

#### Creating Table for comparison 2021 respondent's political spectrum identity against marital status ####

cleaned_gss_2021|>
  tabyl(polviews, marital)|>
  kable(col.names = c(
    "Political Spectrum",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-9
#| tbl-cap: "Marital Status vs. Self-Ascribed Placement on Political of 2018 Respondents"

#### Creating Table for comparison 2021 respondent's political spectrum identity against marital status ####

cleaned_gss_2018|>
  tabyl(polviews, marital)|>
  kable(col.names = c(
    "Political Spectrum",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-10
#| tbl-cap: "Marital Status vs. Self-Ascribed Placement on Political of 2016 Respondents"

#### Creating Table for comparison 2021 respondent's political spectrum identity against marital status ####

cleaned_gss_2016|>
  tabyl(polviews, marital)|>
  kable(col.names = c(
    "Political Spectrum",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-11
#| tbl-cap: "Marital Status vs. Self-Ascribed Placement on Political of 2014 Respondents"

#### Creating Table for comparison 2021 respondent's political spectrum identity against marital status ####

cleaned_gss_2014|>
  tabyl(polviews, marital)|>
  kable(col.names = c(
    "Political Spectrum",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

@@

In this section I briefly describe the **(model(?))** used to investigate the relationship between Political Identity and Marital Status.

@@

$$\hat{y} = \beta_0 + \beta_1$$ 
$\hat{y}$ is marital status 
$\beta_0$ is the political party identity 
$\beta_1$ is the placement on the political spectrum.

\--
